LA ranks

### 2023-03-22 src/la_ranks_n1.Rmd
lisa maps titles
ranks

- add 0s in the df and then calculate the ranks

@@

```{r}
firms <- read_csv("https://www.nomisweb.co.uk/api/v01/dataset/NM_142_1.data.csv?geography=1811939329...1811939332,1811939334...1811939336,1811939338...1811939428,1811939436...1811939442,1811939768,1811939769,1811939443...1811939497,1811939499...1811939501,1811939503,1811939505...1811939507,1811939509...1811939517,1811939519,1811939520,1811939524...1811939570,1811939575...1811939599,1811939601...1811939628,1811939630...1811939634,1811939636...1811939647,1811939649,1811939655...1811939664,1811939667...1811939680,1811939682,1811939683,1811939685,1811939687...1811939704,1811939707,1811939708,1811939710,1811939712...1811939717,1811939719,1811939720,1811939722...1811939730,1811939757...1811939767&date=latestMINUS10&industry=37748736&employment_sizeband=0&legal_status=0&measures=20100") %>% 
  select(GEOGRAPHY_CODE, OBS_VALUE) %>% #GEOGRAPHY_NAME, 
  rename(ladcd = GEOGRAPHY_CODE,
         firms = OBS_VALUE)

@@

la.names <- la@data %>% 
  select(LAD21CD, LAD21NM) %>% 
  rename(ladcd = LAD21CD,
         ladnm = LAD21NM)

df <- df %>% left_join(la.names)
# source: https://geoportal.statistics.gov.uk/
```
## Ranks websites per firm t and 2012 only

```{r}
t <- 1996

@@

  mutate(alpha = ifelse(abs(diff_1st) < 6.875, .8, 0.1)) %>% 
  mutate(alpha = ifelse(is.na(diff_1st), 0.1, alpha)) %>%
  mutate(label = ifelse(alpha==.1, "", ladnm)) %>%

  ggplot(aes(year, rank, group = ladcd, alpha=alpha)) +
  geom_bump(colour = "red") +
  theme(legend.position="none") +
  scale_y_reverse(labels = c(1, 100, 200, 300, 400)) +
  # geom_text(#data = df %>% filter(year == 2012),
  #           aes(x = Inf, label = label), size = 4, hjust = 0)  # x = 2012 + .1
  geom_text_repel(aes(label = label),
                  na.rm = TRUE, 
                  size = 2,
                  nudge_x = 2, nudge_y = 1,
                  direction = "y", hjust = "left")

@@

```{r}
out.path <- paste0(path, "/outputs/ranks/web_2000_2012_only9.png")

@@

  mutate(alpha = ifelse(abs(diff_1st) > 71, .8, 0.1)) %>% 
  mutate(alpha = ifelse(is.na(diff_1st), 0.1, alpha)) %>%
  mutate(label = ifelse(alpha==.1, "", ladnm)) %>%

  ggplot(aes(year, rank, group = ladcd, alpha=alpha)) +
  geom_bump(colour = "red") +
  theme(legend.position="none") +
  scale_y_reverse(labels = c(1, 100, 200, 300, 400)) +
  # geom_text(#data = df %>% filter(year == 2012),
  #           aes(x = Inf, label = label), size = 4, hjust = 0)  # x = 2012 + .1
  geom_text_repel(aes(label = label),
                  na.rm = TRUE, 
                  size = 2,
                  nudge_x = 2, nudge_y = 1,
                  direction = "y", hjust = "left")

>>>>

-

@@

```{r}
firms <- read_csv("https://www.nomisweb.co.uk/api/v01/dataset/NM_142_1.data.csv?geography=1811939329...1811939332,1811939334...1811939336,1811939338...1811939428,1811939436...1811939442,1811939768,1811939769,1811939443...1811939497,1811939499...1811939501,1811939503,1811939505...1811939507,1811939509...1811939517,1811939519,1811939520,1811939524...1811939570,1811939575...1811939599,1811939601...1811939628,1811939630...1811939634,1811939636...1811939647,1811939649,1811939655...1811939664,1811939667...1811939680,1811939682,1811939683,1811939685,1811939687...1811939704,1811939707,1811939708,1811939710,1811939712...1811939717,1811939719,1811939720,1811939722...1811939730,1811939757...1811939767&date=latestMINUS10&industry=37748736&employment_sizeband=0&legal_status=0&measures=20100") %>% 
  dplyr::select(GEOGRAPHY_CODE, OBS_VALUE) %>% #GEOGRAPHY_NAME, 
  rename(ladcd = GEOGRAPHY_CODE,
         firms = OBS_VALUE)

@@

la.names <- la@data %>% 
  dplyr::select(LAD21CD, LAD21NM) %>% 
  rename(ladcd = LAD21CD,
         ladnm = LAD21NM)

df <- df %>% left_join(la.names)
# source: https://geoportal.statistics.gov.uk/
```

## Ranks websites per firm t and 2012 only

```{r}

# change percentile in out.path and mutate(alpha = ifelse(abs(diff_1st)
t <- 2000

@@

  mutate(alpha = ifelse(abs(diff_1st) < 3.75, .8, 0.1)) %>% 
  mutate(alpha = ifelse(is.na(diff_1st), 0.1, alpha)) %>%
  mutate(label = ifelse(alpha==.1, "", ladnm)) %>%

  ggplot(aes(year, rank, group = ladcd, alpha=alpha)) +
  geom_bump(colour = "red") +
  scale_y_reverse(labels = c(1, 100, 200, 300, 400)) +
  # geom_text(#data = df %>% filter(year == 2012),
  #           aes(x = Inf, label = label), size = 4, hjust = 0)  # x = 2012 + .1
  geom_text_repel(aes(label = label),
                  na.rm = TRUE, 
                  size = 2,
                  nudge_x = 2, nudge_y = 1,
                  direction = "y", hjust = "left") +
  theme_minimal() +
  theme(plot.title = element_text(hjust = 0.5)) +
  theme(legend.position="none") 
ggsave(out.path)
```

@@

```{r}
out.path <- paste0(path, "/outputs/ranks/web_2000_2012_only95.png")

@@

  mutate(alpha = ifelse(abs(diff_1st) > 87.75, .8, 0.1)) %>% 
  mutate(alpha = ifelse(is.na(diff_1st), 0.1, alpha)) %>%
  mutate(label = ifelse(alpha==.1, "", ladnm)) %>%

  ggplot(aes(year, rank, group = ladcd, alpha=alpha)) +
  geom_bump(colour = "red") +
  scale_y_reverse(labels = c(1, 100, 200, 300, 400)) +
  # geom_text(#data = df %>% filter(year == 2012),
  #           aes(x = Inf, label = label), size = 4, hjust = 0)  # x = 2012 + .1
  geom_text_repel(aes(label = label),
                  na.rm = TRUE, 
                  size = 2,
                  nudge_x = 2, nudge_y = 1,
                  direction = "y", hjust = "left") +
  theme_minimal() +
  theme(plot.title = element_text(hjust = 0.5)) +
  theme(legend.position="none")
